Revisited hidden weight bit function

### 2024-11-06 RevisedHiddenWeight.tex
more 6

\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
\begin{itemize}
	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
	\[
	\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
	\]
	\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
	\[
	\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
	\]	
\end{itemize}
\end{Prop}

@@

\section{Other parameters}
\subsection{Algebraic immunity of $f$}

\begin{proposition}[Algebraic immunity of $f$]
	Let $n\in \N$ be even, $f$ defined as
	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
	\[\AI(f)\ge \AI(h)-2.\]
\end{proposition}
\begin{proof}
	Let denote by $q$ the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$, it allows to write $h=f+q$. 
	Let $g\neq 0$ be an annihilator of $f+ \varepsilon$ of minimum degree (where $\varepsilon \in \{0,1\}$), then the following holds:
	\[g (1+q) (h+\varepsilon) = g(1+q) (f+\varepsilon + q)=0, \]
	hence $g (1+q)$ is an annihilator of $h+ \varepsilon$. 
	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \le \degg(g)+2$ and we obtain $\degg(g)\ge \AI(h) -2$. 
	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\ge \AI(h)$. 
	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\ge \AI(h)-2$, it allows to conclude $\AI(f)\ge \AI(h)-2$.
\end{proof}

@@

>>>>

%\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
%Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
%\begin{itemize}
%	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
%	\[
%	\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
%	\]
%	\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
%	\[
%	\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
%	\]	
%\end{itemize}
%\end{Prop}

\begin{Prop}[Properties of some functions from $\WD{1}{n}$\label{prop:wwd1}]
	Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
	\begin{itemize}
		\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
		\[
		\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
		\]
		\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
		\[
		\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
		\]	
		\item (\cite{DAM:WCST14}, Theorem $1$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies $\forall n \ge 3$, $\degg(h)=n-1$. 	
	\end{itemize}
\end{Prop}

@@

\section{Other parameters}

\begin{proposition}[Algebraic degree of $f$]
	Let $n\in \N$ be even, greater than $4$, and $f$ defined as in Definition~\ref{def:revHWBF}, the following holds: $\degg(f)= n-1$.
\end{proposition}
\begin{proof}
	We write $f$ as $q+h$ where $q$ is the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$ and $h$ is the HWBF.
	Using Property~\ref{prop:wwd1} Item $3$, $h$ has degree $n-1\ge 3$, and the function $q$ has no monomial of degree higher than $2$, therefore $\degg(f)=\degg(h)=n+1$.

\subsection{Algebraic immunity of $f$}

\begin{proposition}[Algebraic immunity of $f$]
	Let $n\in \N$ be even, $f$ defined (as in Definition~\ref{def:revHWBF}) as
	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
	\[\AI(f)\ge \AI(h)-2.\]
\end{proposition}
\begin{proof}
	Let denote by $q$ the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$, it allows to write $h=f+q$. 
	Let $g\neq 0$ be an annihilator of $f+ \varepsilon$ of minimum degree (where $\varepsilon \in \{0,1\}$), then the following holds:
	\[g (1+q) (h+\varepsilon) = g(1+q) (f+\varepsilon + q)=0, \]
	hence $g (1+q)$ is an annihilator of $h+ \varepsilon$. 
	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \le \degg(g)+2$ and we obtain $\degg(g)\ge \AI(h) -2$. 
	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\ge \AI(h)$. 
	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\ge \AI(h)-2$, it allows to conclude $\AI(f)\ge \AI(h)-2$.
\end{proof}

@@

 \begin{table}[h!]
	 \centering
	 \begin{tabular}{|c|c|c|c|c|}
		 \hline
		 $n$ & Nonlinearity & Is Balanced & Algebraic Degree & Algebraic Immunity \\
		 \hline
		 2   & 1             & False       & 2               & 1                   \\
		 4   & 4             & True        & 3               & 2                   \\
		 6   & 22            & False       & 5               & 3                   \\
		 8   & 102           & True        & 7               & 4                   \\
		 10  & 458           & False       & 9               & 5                   \\
		 12  & 1902          & True        & 11              & 6                   \\
		 14  & 7842          & False       & 13              & 6                   \\
		 16  & 31680         & True        & 15              & —                   \\
		 \hline
		 \end{tabular}
	 \tablecaption{Characteristics of Boolean Functions for Different $n$ Values}
	 \end{table}
